---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HDRegMfd

The goal of this package is to develop high-dimensional regression tools for Hilbert manifold-valued data. 
This package has been implemented for Euclidean, simplex, sphere, SPD matrices with log-Euclidean and affine-invariant metric, functional, BayesHilbert, and Wasserstein space-valued data.

## Installation

You can install this package from GitHub.

```{r}

# devtools::install_github(paste0("cwchoi94/HDRegMfd"))

```

## Usage

This package consists of four high-dimensional regression models: LM, GLM, QM and AM.


### LM

The folder "LM_code" provides source codes for the simulation and real data applications in the following paper:

Choi, C. and Park, B. U. (2025+) High-dimensional Hilbert-Schmidt linear regression with Hilbert
manifold variables. The Annals of Statistics. Accepted.


### GLM

The folder "GLM_code" provides source codes for the simulation and real data applications in the following paper:

Choi, C. and Park, B. U. (2025) High-dimensional generalized linear models for Hilbert manifold
variables. Electronic Journal of Statistics. 19(2), 3979-4053.



### QM


### AM


......


